---
title: "Targets pipeline"
author: "Hidekazu Nagamura"
date: "2023-9-4"
format: 
  html:
    code-fold: true
---

  ## Settings

```{r setup}
library(targets)
library(jagstargets)
library(stantargets)
library(tarchetypes)
library(tidyverse)
library(future)
library(future.callr)
library(future.batchtools)
library(bayesplot)
library(bayestestR)
library(here)
library(ggpubr)
library(ggpp)
library(ggrain)
library(ggdist)
library(ggbeeswarm)
library(see)
library(patchwork)
# library(metaSDT)
library(abind)
library(brms)
library(bridgesampling)
library(stats)
library(rstatix)
library(mc2d)
library(parallel)
library(crew)
library(Hmisc)
library(ggnewscale)
library(RColorBrewer)
source("R/functions.R")
```

```{targets settings, tar_globals = TRUE, tar_interactive = FALSE}
library(jagstargets)
library(stantargets)
library(tarchetypes)
library(here)
library(future)
tar_option_set(packages = c("tarchetypes","here","tidyverse","rstatix","rjags","ggpubr","readxl","dlookr","ggrain","patchwork","future","bayesplot","abind","bayestestR","brms"))
source("R/functions.R")
```

## Non-interactive mode
```{r}
tar_visnetwork()
```

### make
```{r}
tar_option_set(error = "continue", memory = "transient", garbage_collection = TRUE, storage = "worker", retrieval = "worker", format = "qs", controller = crew_controller_local(workers = 30, seconds_idle = 3))
# tar_watch(seconds = 10, outdated = FALSE, targets_only = TRUE)
tar_make(seconds_meta_append = 15, seconds_reporter = 5)
```

## read & preprocess data

```{targets preprocess_exp2, tar_interactive = FALSE}
list(
  tar_target(data_exp2, get_raw_data_exp2() %>% 
               mutate(
                  prev1bet=lag(bet,1),
                  prev2bet=lag(bet,2),
                  prev3bet=lag(bet,3),
                  prev1correctness=lag(correctness,1),
                  prev2correctness=lag(correctness,2),
                  prev3correctness=lag(correctness,3),
                  prev1cnf=lag(cnf,1),
                  prev2cnf=lag(cnf,2),
                  prev3cnf=lag(cnf,3)
                ), deployment = "main"),
  tar_target(preprocess_exp2, preprocess_data(data_exp2, c("condition","difficulty")), deployment = "main")
)
```
```{r}
tar_load(preprocess_exp2)
preprocess_exp2 |> write_csv("csv/preprocess_exp2.csv")
```


extract participant information
```{r}
subj_info <- get_subject_info_exp2()
tar_load(dataframe_condition_difficulty_exp2)
dataframe_condition_difficulty_exp2 <-  dataframe_condition_difficulty_exp2 |> inner_join(subj_info, by = "id")
subj_info <- dataframe_condition_difficulty_exp2 |> ungroup() |>  select(id,age,sex) |> unique()
# library(dlookr)
# eda(subj_info) # exploratory data analysis
```

## analysis
create dataframe in each condition and difficulty
```{targets analysis_exp2, tar_interactive = FALSE}
list(
  tar_target(
    dataframe_condition_difficulty_exp2,
    summarise_data(preprocess_exp2 |> mutate(bet=bet-1), c("id", "difficulty", "condition"))
  )
)
```

```{r}
tar_load(dataframe_condition_difficulty_exp2)
dataframe_condition_difficulty_exp2 <- dataframe_condition_difficulty_exp2 |> 
  rename(
    Difficulty = difficulty, 
    Group = condition,
    Accuracy = accuracy,
    `P(Pre-rating = High)` = bet,
    `Post-rating` = cnf,
    `d'` = d1,
    Score = score
  ) |> 
  mutate(
    Difficulty = factor(if_else(
      Difficulty == "low",
      "Easy",
      "Hard"
    )),
    Group = factor(if_else(
      Group == "bet",
      "Bet",
      "Confidence"
    ), levels = c("Confidence","Bet"))
  )


y <- c("Accuracy","d'","c1","P(Pre-rating = High)","Post-rating","Score","bet_rt","ans_rt","cnf_rt")
pos <- position_dodgenudge(width = 0.2, direction = "split.x")
for (yy in y) {
  p <- plot_between_two_condition_for_paper(dataframe_condition_difficulty_exp2, yy, "Group", "Difficulty", c("Confidence", "Bet"))
  plot(p)

  ggsave(paste0("figure/pdf/",yy,"_exp2.pdf"), dpi = 600, width = 5, height = 5)
}

```

```{r}
tar_load(dataframe_condition_difficulty_exp2)
dataframe_condition_difficulty_exp2 %>% 
  pivot_wider(id_cols = c(id, condition), names_from = difficulty, values_from = c(accuracy, bet, cnf, pre_auroc2, post_auroc2, d1, score, bet_rt, ans_rt, cnf_rt)) %>% 
  write_csv(here("csv/dataframe_condition_difficulty_exp2.csv"))
```

statistical tests for inter-participant variance
```{r}
tar_load(dataframe_condition_difficulty_exp2)
dataframe_condition_difficulty_exp2 |> 
  group_by(difficulty) |>
  levene_test(bet ~ condition) |> 
  adjust_pvalue()
```

## calculate meta-d'

### condition x difficulty

two-way mixed ANOVA
- within: difficulty
- between: condition

#### pre-M-ratio
```{targets metad_pre_between_condition_within_difficulty_exp2, tar_interactive = FALSE}
list(
  tar_target(
    preprocess_metad_pre_between_condition_within_difficulty_exp2,
    preprocess_metad_bet_2way_mixed_anova(preprocess_exp2, c("condition","difficulty"))
  ),
  tar_jags(
    hmetad_pre_between_condition_within_difficulty_exp2,
    jags_files = "jags/Bayes_metad_2way_mixed_ANOVA.txt",
    parameters.to.save = c("muBd_Condition", "lamBd_Condition", "sigD_Condition", "muBd_Condition_prior",
                           "muBd_interaction", "lamBd_interaction", "sigD_interaction", "muBd_interaction_prior",
                           "mu_beta1", "mu_beta1_prior",
                           "Mratio","logMratio","muD","mu_c2","mu_regression",
                           "Bd_Condition","Bd_interaction", "beta1","mu","d1","c1"),
    data = preprocess_metad_pre_between_condition_within_difficulty_exp2,
    n.cluster = 3,
    n.chains = 3,
    n.iter = 30000,
    n.burnin = 5000,
    n.thin = 1,
    refresh = 200,
    progress.bar = "gui"
  )
)
```

#### post-M-ratio
```{targets metad_between_condition_within_difficulty_exp2, tar_interactive = FALSE}
list(
  tar_target(
    preprocess_metad_between_condition_within_difficulty_exp2,
    preprocess_metad_2way_mixed_anova(preprocess_exp2, c("condition","difficulty"))
  ),
  tar_jags(
    hmetad_between_condition_within_difficulty_exp2,
    jags_files = "jags/Bayes_metad_2way_mixed_ANOVA.txt",
    parameters.to.save = c("muBd_Condition", "lamBd_Condition", "sigD_Condition", "muBd_Condition_prior",
                           "muBd_interaction", "lamBd_interaction", "sigD_interaction", "muBd_interaction_prior", 
                           "mu_beta1", "mu_beta1_prior",
                           "Mratio","logMratio","muD","mu_c2","mu_regression",
                           "Bd_Condition","Bd_interaction", "beta1","mu","d1","c1"),
    data = preprocess_metad_between_condition_within_difficulty_exp2,
    n.cluster = 3,
    n.chains = 3,
    n.iter = 30000,
    n.burnin = 5000,
    n.thin = 1,
    refresh = 200,
    progress.bar = "gui"
  )
)
```

### plot mcmc
#### pre-M-ratio
```{r}
parameter_list_2way_mixed_anova <- c(
  # group parameters
  "muBd_Condition", "lamBd_Condition", "sigD_Condition",
  "muD", "mu_c2","mu_beta1","muBd_interaction"
)
tar_load(hmetad_pre_between_condition_within_difficulty_exp2_summary_Bayes_metad_2way_mixed_ANOVA)
tar_load(hmetad_pre_between_condition_within_difficulty_exp2_draws_Bayes_metad_2way_mixed_ANOVA)
check_mcmc(
  hmetad_pre_between_condition_within_difficulty_exp2_summary_Bayes_metad_2way_mixed_ANOVA,
  hmetad_pre_between_condition_within_difficulty_exp2_draws_Bayes_metad_2way_mixed_ANOVA,
  parameter_list_2way_mixed_anova
)
view(hmetad_pre_between_condition_within_difficulty_exp2_summary_Bayes_metad_2way_mixed_ANOVA)

print(paste0("Condition: ",   calculate_pd(hmetad_pre_between_condition_within_difficulty_exp2_draws_Bayes_metad_2way_mixed_ANOVA, "mu_beta1", F)))
print(paste0("Difficulty: ",  calculate_pd(hmetad_pre_between_condition_within_difficulty_exp2_draws_Bayes_metad_2way_mixed_ANOVA, "muBd_Condition", F)))
print(paste0("Interaction: ", calculate_pd(hmetad_pre_between_condition_within_difficulty_exp2_draws_Bayes_metad_2way_mixed_ANOVA, "muBd_interaction", F)))
```

#### post-M-ratio
```{r}
parameter_list_2way_mixed_anova <- c(
  # group parameters
  "muBd_Condition", "lamBd_Condition", "sigD_Condition",
  "muD", "mu_c2","mu_beta1","muBd_interaction"
)
tar_load(hmetad_between_condition_within_difficulty_exp2_summary_Bayes_metad_2way_mixed_ANOVA)
tar_load(hmetad_between_condition_within_difficulty_exp2_draws_Bayes_metad_2way_mixed_ANOVA)
check_mcmc(
  hmetad_between_condition_within_difficulty_exp2_summary_Bayes_metad_2way_mixed_ANOVA,
  hmetad_between_condition_within_difficulty_exp2_draws_Bayes_metad_2way_mixed_ANOVA,
  parameter_list_2way_mixed_anova
)
view(hmetad_between_condition_within_difficulty_exp2_summary_Bayes_metad_2way_mixed_ANOVA)

print(paste0("Condition: ",   calculate_pd(hmetad_between_condition_within_difficulty_exp2_draws_Bayes_metad_2way_mixed_ANOVA, "mu_beta1", F)))
print(paste0("Difficulty: ",  calculate_pd(hmetad_between_condition_within_difficulty_exp2_draws_Bayes_metad_2way_mixed_ANOVA, "muBd_Condition", F)))
print(paste0("Interaction: ", calculate_pd(hmetad_between_condition_within_difficulty_exp2_draws_Bayes_metad_2way_mixed_ANOVA, "muBd_interaction", F)))
```

### plot 95% HDI

#### pre-M-ratio
```{r}
# condition x difficulty
tar_load(hmetad_pre_between_condition_within_difficulty_exp2_draws_Bayes_metad_2way_mixed_ANOVA)
draws_between_condition_within_difficulty_exp2 <-
  hmetad_pre_between_condition_within_difficulty_exp2_draws_Bayes_metad_2way_mixed_ANOVA %>%
    select(
      all_of(starts_with("mu"))
    ) |> 
  rename(
    Interaction = muBd_interaction,
    Group = mu_beta1,
    Difficulty = muBd_Condition,
  )
pars <- c("Group","Difficulty","Interaction")
mcmc_intervals_data(
  draws_between_condition_within_difficulty_exp2, 
  pars = pars, 
  prob = 0.9,
  prob_outer = 0.95
)
color_scheme_set("gray")
p <- mcmc_areas(
  draws_between_condition_within_difficulty_exp2,
  pars = pars,
  prob = 0.95,
  border_size = 2,
) + xlab("Parameter value") + ylab("Parameters") + xlim(c(-25,15)) + theme_pubr(base_size = 24)
plot(p)
ggsave("figure/pdf/posterior_dist_pre_exp2.pdf", dpi = 600, width = 8, height = 5)

```

#### post-M-ratio
```{r}
# condition x difficulty
tar_load(hmetad_between_condition_within_difficulty_exp2_draws_Bayes_metad_2way_mixed_ANOVA)
draws_between_condition_within_difficulty_exp2 <-
  hmetad_between_condition_within_difficulty_exp2_draws_Bayes_metad_2way_mixed_ANOVA %>%
    select(
      all_of(starts_with("mu"))
    ) |> 
  rename(
    Interaction = muBd_interaction,
    Group = mu_beta1,
    Difficulty = muBd_Condition,
  )
pars <- c("Group","Difficulty","Interaction")
mcmc_intervals_data(
  draws_between_condition_within_difficulty_exp2, 
  pars = pars, 
  prob = 0.9,
  prob_outer = 0.95
)
p <- mcmc_areas(
  draws_between_condition_within_difficulty_exp2,
  pars = pars,
  prob = 0.95,
  border_size = 1.5,
  area_method = "scaled height",
) + xlab("Parameter value") + ylab("Parameters") + xlim(c(-25,15)) + theme_pubr(base_size = 24)
plot(p)
ggsave("figure/pdf/posterior_dist_post_exp2.pdf", dpi = 600, width = 8, height = 5)

```

### plot individuals
#### pre-M-ratio
```{r}
# condition x difficulty
tar_load(hmetad_pre_between_condition_within_difficulty_exp2_summary_Bayes_metad_2way_mixed_ANOVA)
tar_load(hmetad_pre_between_condition_within_difficulty_exp2_data)
indiv_draws_between_condition_within_difficulty_exp2_pre <-
  hmetad_pre_between_condition_within_difficulty_exp2_summary_Bayes_metad_2way_mixed_ANOVA %>%
  separate(variable, into = c("name", "idx"), sep = "\\[") %>%
  separate(idx, into = c("id", "difficulty"), sep = ",") %>%
  mutate(
    difficulty = as.numeric(str_sub(difficulty, end = -2)),
  ) %>%
  drop_na(id,difficulty) %>%
  group_by(name,difficulty) %>%
  mutate(
    condition = hmetad_pre_between_condition_within_difficulty_exp2_data$cov,
    condition = if_else(condition == 0, "bet", "cnf")
  ) %>%
  ungroup() %>%
  mutate(
    difficulty = if_else(
      difficulty %% 2 == 0,
      "low",
      "high"
    )
  ) %>%
  select(name, id, condition, difficulty, mean) %>%
  pivot_wider(names_from = name, values_from = mean) %>%
  mutate(Mratio = remove_outliers(Mratio)) %>%
  mutate(logMratio = ifelse(logMratio<10 & logMratio > -100, logMratio, NA)) %>%
  rename(`log(Pre-M-ratio)` = logMratio, Difficulty = difficulty, Group = condition) %>%
  mutate(
    Difficulty = factor(if_else(
      Difficulty == "low",
      "Easy",
      "Hard"
    )),
    Group = factor(if_else(
      Group == "bet",
      "Bet",
      "Confidence"))
  )

p <- plot_between_two_condition_for_paper(indiv_draws_between_condition_within_difficulty_exp2_pre, "log(Pre-M-ratio)", "Group", "Difficulty", c("Bet", "Confidence"))
plot(p)

ggsave(paste0("figure/pdf/pre_logMratio_exp2.pdf"), dpi = 600, width = 5, height = 5)
```

#### post-M-ratio
```{r}
# condition x difficulty
tar_load(hmetad_between_condition_within_difficulty_exp2_summary_Bayes_metad_2way_mixed_ANOVA)
tar_load(hmetad_between_condition_within_difficulty_exp2_data)
indiv_draws_between_condition_within_difficulty_exp2 <-
  hmetad_between_condition_within_difficulty_exp2_summary_Bayes_metad_2way_mixed_ANOVA %>%
  separate(variable, into = c("name", "idx"), sep = "\\[") %>%
  separate(idx, into = c("id", "difficulty"), sep = ",") %>%
  mutate(
    difficulty = as.numeric(str_sub(difficulty, end = -2))
  ) %>%
  drop_na(id,difficulty) %>%
  group_by(name,difficulty) %>%
  mutate(
    condition = hmetad_between_condition_within_difficulty_exp2_data$cov,
    condition = if_else(condition == 0, "bet", "cnf")
  ) %>%
  ungroup() %>%
  mutate(
    difficulty = if_else(
      difficulty %% 2 == 0,
      "low",
      "high"
    )
  ) %>%
  select(name, id, condition, difficulty, mean) %>%
  pivot_wider(names_from = name, values_from = mean) %>%
  mutate(Mratio = remove_outliers(Mratio)) %>%
  mutate(logMratio = ifelse(logMratio<10 & logMratio > -100, logMratio, NA)) %>%
  # group_by(id, condition) %>%
  # mutate(
  #   logMratio = if_else(any(is.na(logMratio)), NA_real_, logMratio),
  #   Mratio = if_else(any(is.na(Mratio)), NA_real_, Mratio)
  # ) %>%
  # ungroup() %>%
  drop_na(everything()) %>%
  rename(`log(Post-M-ratio)` = logMratio, Difficulty = difficulty, Group = condition) %>%
  mutate(
    Difficulty = factor(if_else(
      Difficulty == "low",
      "Easy",
      "Hard"
    )),
    Group = factor(if_else(
      Group == "bet",
      "Bet",
      "Confidence"
    ),levels=c("Confidence","Bet"))
  )

p <- plot_between_two_condition_for_paper(indiv_draws_between_condition_within_difficulty_exp2, "log(Post-M-ratio)", "Group", "Difficulty", c("Confidence", "Bet"))
plot(p)

ggsave(paste0("figure/pdf/post_logMratio_exp2.pdf"), dpi = 600, width = 5, height = 5)

```

export
```{r}
indiv_draws_between_condition_within_difficulty_exp2_pre %>%
  pivot_wider(id_cols = c(id, Group), names_from = Difficulty, values_from = c(d1, `log(Pre-meta-d'/d')`, mu)) %>% 
  write_csv(here("csv/dataframe_metad_pre_exp2.csv"))
indiv_draws_between_condition_within_difficulty_exp2 %>%
  pivot_wider(id_cols = c(id, Group), names_from = Difficulty, values_from = c(d1, `log(Post-meta-d'/d')`, mu)) %>% 
  write_csv(here("csv/dataframe_metad_post_exp2.csv"))

```

### posterior predictive check

```{r}
# condition x difficulty (non-independent priors), posterior confidence
tar_load(dataframe_condition_difficulty_exp2_pre)

tar_load(hmetad_pre_between_condition_within_difficulty_exp2_summary_Bayes_metad_2way_mixed_ANOVA)
tar_load(hmetad_pre_between_condition_within_difficulty_exp2_data)
indiv_draws_between_condition_within_difficulty_exp2_pre <-
  hmetad_pre_between_condition_within_difficulty_exp2_summary_Bayes_metad_2way_mixed_ANOVA %>%
  separate(variable, into = c("name", "idx"), sep = "\\[") %>%
  separate(idx, into = c("id", "difficulty"), sep = ",") %>%
  mutate(
    difficulty = as.numeric(str_sub(difficulty, end = -2)),
  ) %>%
  drop_na(id,difficulty) %>%
  group_by(name,difficulty) %>%
  mutate(
    condition = hmetad_pre_between_condition_within_difficulty_exp2_data$cov,
    condition = if_else(condition < 0, "bet", "cnf")
  ) %>%
  ungroup() %>%
  mutate(
    difficulty = if_else(
      difficulty %% 2 == 1,
      "low",
      "high"
    )
  ) %>%
  select(name, id, condition, difficulty, mean) %>%
  pivot_wider(names_from = name, values_from = mean) %>%
  mutate(
    Mratio = remove_outliers(Mratio)
  ) %>%
  drop_na(everything())

sim_between_condition_within_difficulty_exp2_pre <- indiv_draws_between_condition_within_difficulty_exp2_pre |> 
  group_nest(id, condition, difficulty) |> 
  mutate(simulation = map(data, ~ trialSimulation(d = .x$d1, metad = .x$mu, c = .x$c1, nRatings = 2, nTrials = 1000))) |> 
  select(id, condition, difficulty, simulation) |> 
  unnest(cols = c(simulation)) |> 
  mutate(id = as.numeric(id)) |>
  rename(correctness = Accuracy, bet = Confidence) |> 
  count(id, condition, difficulty, correctness, bet) |> 
  group_by(id, condition, difficulty, correctness) |>
  mutate(proportion = .data$n/sum(.data$n)) |> 
  ungroup() |>
  group_by(condition, difficulty, correctness, bet) |>
  summarise(
    l = quantile(proportion, 0.025),
    m = quantile(proportion, 0.5),
    h = quantile(proportion, 0.975)
  ) |>
  arrange(condition, difficulty, correctness, bet)
  # left_join(dataframe_condition_difficulty_exp2 |> select(-condition, -difficulty, -id), "tmp")

tar_load(preprocess_exp2)
obs_between_condition_within_difficulty_exp2_pre <- preprocess_exp2 |> 
  count(id, condition, difficulty, correctness, bet) |> 
  group_by(id, condition, difficulty, correctness) |>
  mutate(proportion = .data$n/sum(.data$n)) |> 
  ungroup() |> 
  mutate(bet = bet+1)

mean_obs <- obs_between_condition_within_difficulty_exp2_pre |> 
  group_by(condition, difficulty, correctness, bet) |>
  summarise(
    l = quantile(proportion, 0.025),
    m = mean(proportion),
    h = quantile(proportion, 0.975)
  ) |>
  arrange(condition, difficulty, correctness, bet)

  
ggplot() +
  geom_col(
    aes(x = bet, y = m, fill= factor(correctness)), 
    mean_obs, 
    position = "dodge",
    alpha = 0.5
  ) + 
  geom_jitter(
    aes(x = bet, y = proportion, color= factor(correctness), fill = factor(correctness)),
    obs_between_condition_within_difficulty_exp2_pre,
    position = position_jitterdodge(jitter.width = 0.5, jitter.height = 0),
    alpha = 0.8
  ) +
  geom_pointrange(
    aes(x = bet, y = m, ymin = l, ymax = h, fill = factor(correctness)), 
    sim_between_condition_within_difficulty_exp2_pre, 
    position = position_dodge(width = 1) 
  ) +
  facet_grid(condition ~ difficulty)

# p1 <- plot_two_condition(indiv_draws_between_condition_within_difficulty_exp2, "log(Post-meta-d'/d')", "Difficulty", "Group")
# p2 <- raincloudplot_2x2_data(indiv_draws_between_condition_within_difficulty_exp2, "log(Post-meta-d'/d')", "Difficulty", "Group")
# plot(p1+p2)
# ggsave(paste0("figure/post-mratio.svg"), dpi = 300)

```

# sensitivity analysis (for revision)
## read & preprocess data
- exclusion
  - remove only response `nan` or reaction time less than 100 ms
  - remove participants who fixed any responses in each condition
  - remove participants who had fewer than 18 trials in each condition
  
```{targets preprocess_exp2_revision_241224, tar_interactive = FALSE}
list(
  tar_target(data_exp2, get_raw_data_exp2() %>% 
               mutate(
                  prev1bet=lag(bet,1),
                  prev2bet=lag(bet,2),
                  prev3bet=lag(bet,3),
                  prev1correctness=lag(correctness,1),
                  prev2correctness=lag(correctness,2),
                  prev3correctness=lag(correctness,3),
                  prev1cnf=lag(cnf,1),
                  prev2cnf=lag(cnf,2),
                  prev3cnf=lag(cnf,3)
                ), deployment = "main"),
  tar_target(subj_info_exp2, get_subject_info_exp2()),
  tar_target(preprocess_exp2_revise, 
             preprocess_data(
               data_exp2, c("condition","difficulty"),
               remove_fix_behavior = TRUE, 
               remove_few_trial_participants = TRUE, 
               remove_half_accuracy = FALSE,
               remove_fix_bet_correctness = FALSE, 
               remove_fix_cnf_correctness = FALSE
               )),
  tar_target(preprocess_exp2_fix_behavior_few_trial_half_accuracy_fix_bet_cnf, 
             preprocess_data(
               data_exp2, c("condition","difficulty"),
               remove_fix_behavior = FALSE, 
               remove_few_trial_participants = FALSE, 
               remove_half_accuracy = FALSE,
               remove_fix_bet_correctness = FALSE, 
               remove_fix_cnf_correctness = FALSE
               )),
  tar_target(preprocess_exp2_few_trial_half_accuracy_fix_bet_cnf, 
             preprocess_data(
               data_exp2, c("condition","difficulty"),
               remove_fix_behavior = TRUE, 
               remove_few_trial_participants = FALSE, 
               remove_half_accuracy = FALSE,
               remove_fix_bet_correctness = FALSE, 
               remove_fix_cnf_correctness = FALSE
               )),
  tar_target(preprocess_exp2_half_accuracy_fix_bet_cnf, 
             preprocess_data(
               data_exp2, c("condition","difficulty"),
               remove_fix_behavior = TRUE, 
               remove_few_trial_participants = TRUE, 
               remove_half_accuracy = FALSE,
               remove_fix_bet_correctness = FALSE, 
               remove_fix_cnf_correctness = FALSE
               )),
  tar_target(preprocess_exp2_few_trial_fix_bet_cnf, 
             preprocess_data(
               data_exp2, c("condition","difficulty"),
               remove_fix_behavior = TRUE, 
               remove_few_trial_participants = FALSE, 
               remove_half_accuracy = TRUE,
               remove_fix_bet_correctness = FALSE, 
               remove_fix_cnf_correctness = FALSE
               )),
  tar_target(preprocess_exp2_few_trial_half_accuracy, 
             preprocess_data(
               data_exp2, c("condition","difficulty"),
               remove_fix_behavior = TRUE, 
               remove_few_trial_participants = FALSE, 
               remove_half_accuracy = FALSE,
               remove_fix_bet_correctness = TRUE, 
               remove_fix_cnf_correctness = TRUE
               )),
  tar_target(preprocess_exp2_half_accuracy, 
             preprocess_data(
               data_exp2, c("condition","difficulty"),
               remove_fix_behavior = TRUE, 
               remove_few_trial_participants = TRUE, 
               remove_half_accuracy = FALSE,
               remove_fix_bet_correctness = TRUE, 
               remove_fix_cnf_correctness = TRUE
               )),
  tar_target(preprocess_exp2_few_trial, 
             preprocess_data(
               data_exp2, c("condition","difficulty"),
               remove_fix_behavior = TRUE, 
               remove_few_trial_participants = FALSE, 
               remove_half_accuracy = TRUE,
               remove_fix_bet_correctness = TRUE, 
               remove_fix_cnf_correctness = TRUE
               )),
  tar_target(preprocess_exp2, 
             preprocess_data(
               data_exp2, c("condition","difficulty"),
               remove_fix_behavior = TRUE, 
               remove_few_trial_participants = TRUE, 
               remove_half_accuracy = TRUE,
               remove_fix_bet_correctness = TRUE, 
               remove_fix_cnf_correctness = TRUE
               ))
)
```


## analysis
create dataframe in each condition and difficulty
```{targets analysis_for_revision, tar_interactive = FALSE}
list(
  tar_target(
    dataframe_condition_difficulty_revise,
    summarise_data(preprocess_exp2_revise |> mutate(bet=bet-1), c("id", "difficulty", "condition"))
  ),
  tar_target(
    dataframe_bet_revise,
    summarise_data(preprocess_exp2_revise |> mutate(bet=bet-1), c("id", "bet"))
  ),
  tar_target(
    dataframe_condition_difficulty_fix_behavior_few_trial_half_accuracy_fix_bet_cnf,
    summarise_data(preprocess_exp2_fix_behavior_few_trial_half_accuracy_fix_bet_cnf |> mutate(bet=bet-1), c("id", "difficulty", "condition"))
  ),
  tar_target(
    dataframe_bet_fix_behavior_few_trial_half_accuracy_fix_bet_cnf,
    summarise_data(preprocess_exp2_fix_behavior_few_trial_half_accuracy_fix_bet_cnf |> mutate(bet=bet-1), c("id", "bet"))
  ),
  tar_target(
    dataframe_condition_difficulty_few_trial_half_accuracy_fix_bet_cnf,
    summarise_data(preprocess_exp2_few_trial_half_accuracy_fix_bet_cnf |> mutate(bet=bet-1), c("id", "difficulty", "condition"))
  ),
  tar_target(
    dataframe_condition_difficulty_half_accuracy_fix_bet_cnf,
    summarise_data(preprocess_exp2_half_accuracy_fix_bet_cnf |> mutate(bet=bet-1), c("id", "difficulty", "condition"))
  ),
  tar_target(
    dataframe_condition_difficulty_few_trial_fix_bet_cnf,
    summarise_data(preprocess_exp2_few_trial_fix_bet_cnf |> mutate(bet=bet-1), c("id", "difficulty", "condition"))
  ),
  tar_target(
    dataframe_condition_difficulty_few_trial_half_accuracy,
    summarise_data(preprocess_exp2_few_trial_half_accuracy |> mutate(bet=bet-1), c("id", "difficulty", "condition"))
  ),
  tar_target(
    dataframe_condition_difficulty_half_accuracy,
    summarise_data(preprocess_exp2_half_accuracy |> mutate(bet=bet-1), c("id", "difficulty", "condition"))
  ),
  tar_target(
    dataframe_condition_difficulty_few_trial,
    summarise_data(preprocess_exp2_few_trial |> mutate(bet=bet-1), c("id", "difficulty", "condition"))
  ),
  tar_target(
    dataframe_condition_difficulty,
    summarise_data(preprocess_exp2 |> mutate(bet=bet-1), c("id", "difficulty", "condition"))
  )
)
```

```{r}
print_sample_size <- function(dataframe_name) {
  original_sample_size <- 237
  tar_load(!!sym(dataframe_name))
  dataframe <- get(dataframe_name)
  tar_load(subj_info_exp2)

  subj_data <- dataframe |> select(id, condition) |> unique() |> 
    left_join(subj_info_exp2, by = "id")
  
  sample_size <- subj_data |> nrow()
  n_bet <- subj_data |> filter(condition == "bet") |> nrow()
  n_cnf <- subj_data |> filter(condition == "cnf") |> nrow()
  n_female <- subj_data |> filter(sex == "female") |> nrow()
  n_male   <- subj_data |> filter(sex == "male")   |> nrow()
  age_mean <- subj_data |> pull(age) |> mean() |> round(1)
  age_sd   <- subj_data |> pull(age) |> sd() |> round(1)
  age_min  <- subj_data |> pull(age) |> min()
  age_max  <- subj_data |> pull(age) |> max()
  
  print(paste0("N = ", sample_size," (",round(sample_size/original_sample_size*100),"% of ", original_sample_size , ")"))
  print(paste0("Confidence: N = ", n_cnf, "; Bet: N = ", n_bet))
  print(paste0("female: N = ", n_female, "; male: N = ", n_male))
  print(paste0("aged ", age_min, "-", age_max, " years"))
  print(paste0(age_mean, "±", age_sd, " (mean±SD) years"))
}
```

### Participant & Table 1

```{r}
print_sample_size("preprocess_exp2_revise")
```

```{r}
print_sample_size("preprocess_exp2_fix_behavior_few_trial_half_accuracy_fix_bet_cnf")
```

```{r}
basic_analysis_for_revision <- function(dataframe_name, criteria) {
  tar_load(!!sym(dataframe_name))
  
  # arrange dataframe for JASP
  dataframe <- get(dataframe_name)
  dataframe |> 
    pivot_wider(id_cols = c(id, condition), names_from = difficulty, values_from = c(accuracy, bet, cnf, pre_auroc2, post_auroc2, d1, score, bet_rt, ans_rt, cnf_rt)) |> 
    write_csv(here(paste0("csv/dataframe_condition_difficulty_exp2_",criteria,".csv")))
  
  # rename columns for creating figures
  dataframe <- get(dataframe_name) |> 
    rename(
      Difficulty = difficulty, 
      Group = condition,
      Accuracy = accuracy,
      `P(Pre-rating = High)` = bet,
      `Post-rating` = cnf,
      `d'` = d1,
      Score = score
    ) |> 
    mutate(
      Difficulty = factor(if_else(
        Difficulty == "low",
        "Easy",
        "Hard"
      )),
      Group = factor(if_else(
        Group == "bet",
        "Bet",
        "Confidence"
      ), levels = c("Confidence","Bet"))
    )
  
  # plot
  y <- c("Accuracy","d'","c1","P(Pre-rating = High)","Post-rating","Score","bet_rt","ans_rt","cnf_rt")
  pos <- position_dodgenudge(width = 0.2, direction = "split.x")
  for (yy in y) {
    p <- plot_between_two_condition_for_paper(dataframe, yy, "Group", "Difficulty", c("Confidence", "Bet"))
    plot(p)
  
    ggsave(paste0("figure/pdf/",yy,"_exp2_",criteria,".pdf"), dpi = 600, width = 5, height = 5)
  }
  
  # statistical tests
  # dataframe |> 
  #   anova_test(Accuracy ~ Group * Difficulty)
  # dataframe |> 
  #   anova_test(`P(Pre-rating = High)` ~ Group * Difficulty)
  # dataframe |> 
  #   anova_test(`Post-rating` ~ Group * Difficulty)
  ## for inter-participant variance
  dataframe |> 
    group_by(Difficulty) |>
    levene_test(`P(Pre-rating = High)` ~ Group) |> 
    adjust_pvalue()
}
```

### Figure 2
```{r}
basic_analysis_for_revision("dataframe_condition_difficulty_revise", "revise")
```

```{r}
basic_analysis_for_revision("dataframe_condition_difficulty_fix_behavior_few_trial_half_accuracy_fix_bet_cnf", "fix_behavior_few_trial_half_accuracy_fix_bet_cnf")
```

```{r}
cnf_analysis_by_bet <- function(dataframe_name, criteria) {
  tar_load(!!sym(dataframe_name))
  
  # arrange dataframe for JASP
  dataframe <- get(dataframe_name)
  
  dataframe |> 
    pivot_wider(id_cols = c(id), names_from = bet, values_from = c(accuracy, cnf, pre_auroc2, post_auroc2, d1, score, bet_rt, ans_rt, cnf_rt)) |> 
    write_csv(here(paste0("csv/dataframe_bet_",criteria,"_exp2_revise.csv")))
  
  dataframe <- dataframe |> 
    rename(
      Accuracy = accuracy,
      `Pre-rating` = bet,
      `Post-rating` = cnf,
      `d'` = d1,
      Score = score
    ) |> 
    mutate(
      `Pre-rating` = factor(if_else(
        `Pre-rating` == 0,
        "Low",
        "High"
      ), levels = c("Low", "High"))
    )
  
  p <- plot_within_one_condition_for_paper(dataframe, "Post-rating", "Pre-rating")
  plot(p)
  
  ggsave(paste0("figure/pdf/fig4_exp2_",criteria,".pdf"), dpi = 600, width = 5, height = 5)
  
}
```


### Figure 4
```{r}
cnf_analysis_by_bet("dataframe_bet_revise", "revise")
```


```{r}
cnf_analysis_by_bet("dataframe_bet_fix_behavior_few_trial_half_accuracy_fix_bet_cnf", "fix_behavior_few_trial_half_accuracy_fix_bet_cnf")
```

## calculate meta-d'

### condition x difficulty

two-way mixed ANOVA
- within: difficulty
- between: condition

#### pre-M-ratio

```{targets preprocess_metad_pre_between_condition_within_difficulty_exp2_for_revision, tar_interactive = FALSE}
list(
  tar_target(
    preprocess_metad_pre_between_condition_within_difficulty_exp2_revise,
    preprocess_metad_bet_2way_mixed_anova(preprocess_exp2_revise, c("condition", "difficulty"))
  ),
  tar_target(
    preprocess_metad_pre_between_condition_within_difficulty_exp2_fix_behavior_few_trial_half_accuracy_fix_bet_cnf,
    preprocess_metad_bet_2way_mixed_anova(preprocess_exp2_fix_behavior_few_trial_half_accuracy_fix_bet_cnf, c("condition", "difficulty"))
  ),
  tar_target(
    preprocess_metad_pre_between_condition_within_difficulty_exp2_few_trial_half_accuracy_fix_bet_cnf,
    preprocess_metad_bet_2way_mixed_anova(preprocess_exp2_few_trial_half_accuracy_fix_bet_cnf, c("condition", "difficulty"))
  ),
  tar_target(
    preprocess_metad_pre_between_condition_within_difficulty_exp2_half_accuracy_fix_bet_cnf,
    preprocess_metad_bet_2way_mixed_anova(preprocess_exp2_half_accuracy_fix_bet_cnf, c("condition", "difficulty"))
  ),
  tar_target(
    preprocess_metad_pre_between_condition_within_difficulty_exp2_few_trial_fix_bet_cnf,
    preprocess_metad_bet_2way_mixed_anova(preprocess_exp2_few_trial_fix_bet_cnf, c("condition", "difficulty"))
  ),
  tar_target(
    preprocess_metad_pre_between_condition_within_difficulty_exp2_few_trial_half_accuracy,
    preprocess_metad_bet_2way_mixed_anova(preprocess_exp2_few_trial_half_accuracy, c("condition", "difficulty"))
  ),
  tar_target(
    preprocess_metad_pre_between_condition_within_difficulty_exp2_half_accuracy,
    preprocess_metad_bet_2way_mixed_anova(preprocess_exp2_half_accuracy, c("condition", "difficulty"))
  ),
  tar_target(
    preprocess_metad_pre_between_condition_within_difficulty_exp2_few_trial,
    preprocess_metad_bet_2way_mixed_anova(preprocess_exp2_few_trial, c("condition", "difficulty"))
  ),
  tar_target(
    preprocess_metad_pre_between_condition_within_difficulty_exp2,
    preprocess_metad_bet_2way_mixed_anova(preprocess_exp2, c("condition", "difficulty"))
  )
)
```

```{targets metad_pre_between_condition_within_difficulty_exp2_for_revision, tar_interactive = FALSE}
list(
  tar_jags(
    hmetad_pre_between_condition_within_difficulty_exp2_revise,
    jags_files = "jags/Bayes_metad_2way_mixed_ANOVA.txt",
    parameters.to.save = c("muBd_Condition", "lamBd_Condition", "sigD_Condition", "muBd_Condition_prior",
                           "muBd_interaction", "lamBd_interaction", "sigD_interaction", "muBd_interaction_prior",
                           "mu_beta1", "mu_beta1_prior",
                           "Mratio","logMratio","muD","mu_c2","mu_regression",
                           "Bd_Condition","Bd_interaction", "beta1","mu","d1","c1"),
    data = preprocess_metad_pre_between_condition_within_difficulty_exp2_revise,
    n.cluster = 3,
    n.chains = 3,
    n.iter = 10000,
    n.burnin = 1000,
    n.thin = 1,
    refresh = 200,
    error = "continue", 
    progress.bar = "gui"
  ),
  tar_jags(
    hmetad_pre_between_condition_within_difficulty_exp2_fix_behavior_few_trial_half_accuracy_fix_bet_cnf,
    jags_files = "jags/Bayes_metad_2way_mixed_ANOVA.txt",
    parameters.to.save = c("muBd_Condition", "lamBd_Condition", "sigD_Condition", "muBd_Condition_prior",
                           "muBd_interaction", "lamBd_interaction", "sigD_interaction", "muBd_interaction_prior",
                           "mu_beta1", "mu_beta1_prior",
                           "Mratio","logMratio","muD","mu_c2","mu_regression",
                           "Bd_Condition","Bd_interaction", "beta1","mu","d1","c1"),
    data = preprocess_metad_pre_between_condition_within_difficulty_exp2_fix_behavior_few_trial_half_accuracy_fix_bet_cnf,
    n.cluster = 3,
    n.chains = 3,
    n.iter = 10000,
    n.burnin = 1000,
    n.thin = 1,
    refresh = 200,
    error = "continue", 
    progress.bar = "gui"
  ),
  tar_jags(
    hmetad_pre_between_condition_within_difficulty_exp2_few_trial_half_accuracy_fix_bet_cnf,
    jags_files = "jags/Bayes_metad_2way_mixed_ANOVA.txt",
    parameters.to.save = c("muBd_Condition", "lamBd_Condition", "sigD_Condition", "muBd_Condition_prior",
                           "muBd_interaction", "lamBd_interaction", "sigD_interaction", "muBd_interaction_prior",
                           "mu_beta1", "mu_beta1_prior",
                           "Mratio","logMratio","muD","mu_c2","mu_regression",
                           "Bd_Condition","Bd_interaction", "beta1","mu","d1","c1"),
    data = preprocess_metad_pre_between_condition_within_difficulty_exp2_few_trial_half_accuracy_fix_bet_cnf,
    n.cluster = 3,
    n.chains = 3,
    n.iter = 10000,
    n.burnin = 1000,
    n.thin = 1,
    refresh = 200,
    error = "continue", 
    progress.bar = "gui"
  ),
  tar_jags(
    hmetad_pre_between_condition_within_difficulty_exp2_half_accuracy_fix_bet_cnf,
    jags_files = "jags/Bayes_metad_2way_mixed_ANOVA.txt",
    parameters.to.save = c("muBd_Condition", "lamBd_Condition", "sigD_Condition", "muBd_Condition_prior",
                           "muBd_interaction", "lamBd_interaction", "sigD_interaction", "muBd_interaction_prior",
                           "mu_beta1", "mu_beta1_prior",
                           "Mratio","logMratio","muD","mu_c2","mu_regression",
                           "Bd_Condition","Bd_interaction", "beta1","mu","d1","c1"),
    data = preprocess_metad_pre_between_condition_within_difficulty_exp2_half_accuracy_fix_bet_cnf,
    n.cluster = 3,
    n.chains = 3,
    n.iter = 10000,
    n.burnin = 1000,
    n.thin = 1,
    refresh = 200,
    error = "continue", 
    progress.bar = "gui"
  ),
  tar_jags(
    hmetad_pre_between_condition_within_difficulty_exp2_few_trial_fix_bet_cnf,
    jags_files = "jags/Bayes_metad_2way_mixed_ANOVA.txt",
    parameters.to.save = c("muBd_Condition", "lamBd_Condition", "sigD_Condition", "muBd_Condition_prior",
                           "muBd_interaction", "lamBd_interaction", "sigD_interaction", "muBd_interaction_prior",
                           "mu_beta1", "mu_beta1_prior",
                           "Mratio","logMratio","muD","mu_c2","mu_regression",
                           "Bd_Condition","Bd_interaction", "beta1","mu","d1","c1"),
    data = preprocess_metad_pre_between_condition_within_difficulty_exp2_few_trial_fix_bet_cnf,
    n.cluster = 3,
    n.chains = 3,
    n.iter = 10000,
    n.burnin = 1000,
    n.thin = 1,
    refresh = 200,
    error = "continue", 
    progress.bar = "gui"
  ),
  tar_jags(
    hmetad_pre_between_condition_within_difficulty_exp2_few_trial_half_accuracy,
    jags_files = "jags/Bayes_metad_2way_mixed_ANOVA.txt",
    parameters.to.save = c("muBd_Condition", "lamBd_Condition", "sigD_Condition", "muBd_Condition_prior",
                           "muBd_interaction", "lamBd_interaction", "sigD_interaction", "muBd_interaction_prior",
                           "mu_beta1", "mu_beta1_prior",
                           "Mratio","logMratio","muD","mu_c2","mu_regression",
                           "Bd_Condition","Bd_interaction", "beta1","mu","d1","c1"),
    data = preprocess_metad_pre_between_condition_within_difficulty_exp2_few_trial_half_accuracy,
    n.cluster = 3,
    n.chains = 3,
    n.iter = 10000,
    n.burnin = 1000,
    n.thin = 1,
    refresh = 200,
    error = "continue", 
    progress.bar = "gui"
  ),
  tar_jags(
    hmetad_pre_between_condition_within_difficulty_exp2_half_accuracy,
    jags_files = "jags/Bayes_metad_2way_mixed_ANOVA.txt",
    parameters.to.save = c("muBd_Condition", "lamBd_Condition", "sigD_Condition", "muBd_Condition_prior",
                           "muBd_interaction", "lamBd_interaction", "sigD_interaction", "muBd_interaction_prior",
                           "mu_beta1", "mu_beta1_prior",
                           "Mratio","logMratio","muD","mu_c2","mu_regression",
                           "Bd_Condition","Bd_interaction", "beta1","mu","d1","c1"),
    data = preprocess_metad_pre_between_condition_within_difficulty_exp2_half_accuracy,
    n.cluster = 3,
    n.chains = 3,
    n.iter = 10000,
    n.burnin = 1000,
    n.thin = 1,
    refresh = 200,
    error = "continue", 
    progress.bar = "gui"
  ),
  tar_jags(
    hmetad_pre_between_condition_within_difficulty_exp2_few_trial,
    jags_files = "jags/Bayes_metad_2way_mixed_ANOVA.txt",
    parameters.to.save = c("muBd_Condition", "lamBd_Condition", "sigD_Condition", "muBd_Condition_prior",
                           "muBd_interaction", "lamBd_interaction", "sigD_interaction", "muBd_interaction_prior",
                           "mu_beta1", "mu_beta1_prior",
                           "Mratio","logMratio","muD","mu_c2","mu_regression",
                           "Bd_Condition","Bd_interaction", "beta1","mu","d1","c1"),
    data = preprocess_metad_pre_between_condition_within_difficulty_exp2_few_trial,
    n.cluster = 3,
    n.chains = 3,
    n.iter = 10000,
    n.burnin = 1000,
    n.thin = 1,
    refresh = 200,
    error = "continue", 
    progress.bar = "gui"
  ),
  tar_jags(
    hmetad_pre_between_condition_within_difficulty_exp2,
    jags_files = "jags/Bayes_metad_2way_mixed_ANOVA.txt",
    parameters.to.save = c("muBd_Condition", "lamBd_Condition", "sigD_Condition", "muBd_Condition_prior",
                           "muBd_interaction", "lamBd_interaction", "sigD_interaction", "muBd_interaction_prior",
                           "mu_beta1", "mu_beta1_prior",
                           "Mratio","logMratio","muD","mu_c2","mu_regression",
                           "Bd_Condition","Bd_interaction", "beta1","mu","d1","c1"),
    data = preprocess_metad_pre_between_condition_within_difficulty_exp2,
    n.cluster = 3,
    n.chains = 3,
    n.iter = 10000,
    n.burnin = 1000,
    n.thin = 1,
    refresh = 200,
    error = "continue", 
    progress.bar = "gui"
  )
)
```

#### post-M-ratio

```{targets preprocess_metad_between_condition_within_difficulty_exp2_for_revision, tar_interactive = FALSE}
list(
  tar_target(
    preprocess_metad_between_condition_within_difficulty_exp2_revise,
    preprocess_metad_2way_mixed_anova(preprocess_exp2_revise, c("condition", "difficulty"))
  ),
  tar_target(
    preprocess_metad_between_condition_within_difficulty_exp2_fix_behavior_few_trial_half_accuracy_fix_bet_cnf,
    preprocess_metad_2way_mixed_anova(preprocess_exp2_fix_behavior_few_trial_half_accuracy_fix_bet_cnf, c("condition", "difficulty"))
  ),
  tar_target(
    preprocess_metad_between_condition_within_difficulty_exp2_few_trial_half_accuracy_fix_bet_cnf,
    preprocess_metad_2way_mixed_anova(preprocess_exp2_few_trial_half_accuracy_fix_bet_cnf, c("condition", "difficulty"))
  ),
  tar_target(
    preprocess_metad_between_condition_within_difficulty_exp2_half_accuracy_fix_bet_cnf,
    preprocess_metad_2way_mixed_anova(preprocess_exp2_half_accuracy_fix_bet_cnf, c("condition", "difficulty"))
  ),
  tar_target(
    preprocess_metad_between_condition_within_difficulty_exp2_few_trial_fix_bet_cnf,
    preprocess_metad_2way_mixed_anova(preprocess_exp2_few_trial_fix_bet_cnf, c("condition", "difficulty"))
  ),
  tar_target(
    preprocess_metad_between_condition_within_difficulty_exp2_few_trial_half_accuracy,
    preprocess_metad_2way_mixed_anova(preprocess_exp2_few_trial_half_accuracy, c("condition", "difficulty"))
  ),
  tar_target(
    preprocess_metad_between_condition_within_difficulty_exp2_half_accuracy,
    preprocess_metad_2way_mixed_anova(preprocess_exp2_half_accuracy, c("condition", "difficulty"))
  ),
  tar_target(
    preprocess_metad_between_condition_within_difficulty_exp2_few_trial,
    preprocess_metad_2way_mixed_anova(preprocess_exp2_few_trial, c("condition", "difficulty"))
  ),
  tar_target(
    preprocess_metad_between_condition_within_difficulty_exp2,
    preprocess_metad_2way_mixed_anova(preprocess_exp2, c("condition", "difficulty"))
  )
)
```

```{targets metad_between_condition_within_difficulty_exp2_for_revision, tar_interactive = FALSE}
list(
  tar_jags(
    hmetad_between_condition_within_difficulty_exp2_revise,
    jags_files = "jags/Bayes_metad_2way_mixed_ANOVA.txt",
    parameters.to.save = c("muBd_Condition", "lamBd_Condition", "sigD_Condition", "muBd_Condition_prior",
                           "muBd_interaction", "lamBd_interaction", "sigD_interaction", "muBd_interaction_prior",
                           "mu_beta1", "mu_beta1_prior",
                           "Mratio","logMratio","muD","mu_c2","mu_regression",
                           "Bd_Condition","Bd_interaction", "beta1","mu","d1","c1"),
    data = preprocess_metad_between_condition_within_difficulty_exp2_revise,
    n.cluster = 3,
    n.chains = 3,
    n.iter = 10000,
    n.burnin = 1000,
    n.thin = 1,
    refresh = 200,
    error = "continue", 
    progress.bar = "gui"
  ),
  tar_jags(
    hmetad_between_condition_within_difficulty_exp2_fix_behavior_few_trial_half_accuracy_fix_bet_cnf,
    jags_files = "jags/Bayes_metad_2way_mixed_ANOVA.txt",
    parameters.to.save = c("muBd_Condition", "lamBd_Condition", "sigD_Condition", "muBd_Condition_prior",
                           "muBd_interaction", "lamBd_interaction", "sigD_interaction", "muBd_interaction_prior",
                           "mu_beta1", "mu_beta1_prior",
                           "Mratio","logMratio","muD","mu_c2","mu_regression",
                           "Bd_Condition","Bd_interaction", "beta1","mu","d1","c1"),
    data = preprocess_metad_between_condition_within_difficulty_exp2_fix_behavior_few_trial_half_accuracy_fix_bet_cnf,
    n.cluster = 3,
    n.chains = 3,
    n.iter = 10000,
    n.burnin = 1000,
    n.thin = 1,
    refresh = 200,
    error = "continue", 
    progress.bar = "gui"
  ),
  tar_jags(
    hmetad_between_condition_within_difficulty_exp2_few_trial_half_accuracy_fix_bet_cnf,
    jags_files = "jags/Bayes_metad_2way_mixed_ANOVA.txt",
    parameters.to.save = c("muBd_Condition", "lamBd_Condition", "sigD_Condition", "muBd_Condition_prior",
                           "muBd_interaction", "lamBd_interaction", "sigD_interaction", "muBd_interaction_prior",
                           "mu_beta1", "mu_beta1_prior",
                           "Mratio","logMratio","muD","mu_c2","mu_regression",
                           "Bd_Condition","Bd_interaction", "beta1","mu","d1","c1"),
    data = preprocess_metad_between_condition_within_difficulty_exp2_few_trial_half_accuracy_fix_bet_cnf,
    n.cluster = 3,
    n.chains = 3,
    n.iter = 10000,
    n.burnin = 1000,
    n.thin = 1,
    refresh = 200,
    error = "continue", 
    progress.bar = "gui"
  ),
  tar_jags(
    hmetad_between_condition_within_difficulty_exp2_half_accuracy_fix_bet_cnf,
    jags_files = "jags/Bayes_metad_2way_mixed_ANOVA.txt",
    parameters.to.save = c("muBd_Condition", "lamBd_Condition", "sigD_Condition", "muBd_Condition_prior",
                           "muBd_interaction", "lamBd_interaction", "sigD_interaction", "muBd_interaction_prior",
                           "mu_beta1", "mu_beta1_prior",
                           "Mratio","logMratio","muD","mu_c2","mu_regression",
                           "Bd_Condition","Bd_interaction", "beta1","mu","d1","c1"),
    data = preprocess_metad_between_condition_within_difficulty_exp2_half_accuracy_fix_bet_cnf,
    n.cluster = 3,
    n.chains = 3,
    n.iter = 10000,
    n.burnin = 1000,
    n.thin = 1,
    refresh = 200,
    error = "continue", 
    progress.bar = "gui"
  ),
  tar_jags(
    hmetad_between_condition_within_difficulty_exp2_few_trial_fix_bet_cnf,
    jags_files = "jags/Bayes_metad_2way_mixed_ANOVA.txt",
    parameters.to.save = c("muBd_Condition", "lamBd_Condition", "sigD_Condition", "muBd_Condition_prior",
                           "muBd_interaction", "lamBd_interaction", "sigD_interaction", "muBd_interaction_prior",
                           "mu_beta1", "mu_beta1_prior",
                           "Mratio","logMratio","muD","mu_c2","mu_regression",
                           "Bd_Condition","Bd_interaction", "beta1","mu","d1","c1"),
    data = preprocess_metad_between_condition_within_difficulty_exp2_few_trial_fix_bet_cnf,
    n.cluster = 3,
    n.chains = 3,
    n.iter = 10000,
    n.burnin = 1000,
    n.thin = 1,
    refresh = 200,
    error = "continue", 
    progress.bar = "gui"
  ),
  tar_jags(
    hmetad_between_condition_within_difficulty_exp2_few_trial_half_accuracy,
    jags_files = "jags/Bayes_metad_2way_mixed_ANOVA.txt",
    parameters.to.save = c("muBd_Condition", "lamBd_Condition", "sigD_Condition", "muBd_Condition_prior",
                           "muBd_interaction", "lamBd_interaction", "sigD_interaction", "muBd_interaction_prior",
                           "mu_beta1", "mu_beta1_prior",
                           "Mratio","logMratio","muD","mu_c2","mu_regression",
                           "Bd_Condition","Bd_interaction", "beta1","mu","d1","c1"),
    data = preprocess_metad_between_condition_within_difficulty_exp2_few_trial_half_accuracy,
    n.cluster = 3,
    n.chains = 3,
    n.iter = 10000,
    n.burnin = 1000,
    n.thin = 1,
    refresh = 200,
    error = "continue", 
    progress.bar = "gui"
  ),
  tar_jags(
    hmetad_between_condition_within_difficulty_exp2_half_accuracy,
    jags_files = "jags/Bayes_metad_2way_mixed_ANOVA.txt",
    parameters.to.save = c("muBd_Condition", "lamBd_Condition", "sigD_Condition", "muBd_Condition_prior",
                           "muBd_interaction", "lamBd_interaction", "sigD_interaction", "muBd_interaction_prior",
                           "mu_beta1", "mu_beta1_prior",
                           "Mratio","logMratio","muD","mu_c2","mu_regression",
                           "Bd_Condition","Bd_interaction", "beta1","mu","d1","c1"),
    data = preprocess_metad_between_condition_within_difficulty_exp2_half_accuracy,
    n.cluster = 3,
    n.chains = 3,
    n.iter = 10000,
    n.burnin = 1000,
    n.thin = 1,
    refresh = 200,
    error = "continue", 
    progress.bar = "gui"
  ),
  tar_jags(
    hmetad_between_condition_within_difficulty_exp2_few_trial,
    jags_files = "jags/Bayes_metad_2way_mixed_ANOVA.txt",
    parameters.to.save = c("muBd_Condition", "lamBd_Condition", "sigD_Condition", "muBd_Condition_prior",
                           "muBd_interaction", "lamBd_interaction", "sigD_interaction", "muBd_interaction_prior",
                           "mu_beta1", "mu_beta1_prior",
                           "Mratio","logMratio","muD","mu_c2","mu_regression",
                           "Bd_Condition","Bd_interaction", "beta1","mu","d1","c1"),
    data = preprocess_metad_between_condition_within_difficulty_exp2_few_trial,
    n.cluster = 3,
    n.chains = 3,
    n.iter = 10000,
    n.burnin = 1000,
    n.thin = 1,
    refresh = 200,
    error = "continue", 
    progress.bar = "gui"
  ),
  tar_jags(
    hmetad_between_condition_within_difficulty_exp2,
    jags_files = "jags/Bayes_metad_2way_mixed_ANOVA.txt",
    parameters.to.save = c("muBd_Condition", "lamBd_Condition", "sigD_Condition", "muBd_Condition_prior",
                           "muBd_interaction", "lamBd_interaction", "sigD_interaction", "muBd_interaction_prior",
                           "mu_beta1", "mu_beta1_prior",
                           "Mratio","logMratio","muD","mu_c2","mu_regression",
                           "Bd_Condition","Bd_interaction", "beta1","mu","d1","c1"),
    data = preprocess_metad_between_condition_within_difficulty_exp2,
    n.cluster = 3,
    n.chains = 3,
    n.iter = 10000,
    n.burnin = 1000,
    n.thin = 1,
    refresh = 200,
    error = "continue", 
    progress.bar = "gui"
  )
)
```

### plot mcmc
```{r}
plot_mcmc <- function(summary_name, draws_name, parameter_list) {
  tar_load(summary_name)
  tar_load(draws_name)
  summary <- get(summary_name)
  draws <- get(draws_name)
  
  check_mcmc(summary, draws, parameter_list)
  # view(summary)
  print(paste0("Instruction: pd = ",   calculate_pd(draws, "mu_beta1", F)))
  print(paste0("Difficulty: pd = ",  calculate_pd(draws, "muBd_Condition", F)))
  print(paste0("Interaction: pd = ", calculate_pd(draws, "muBd_interaction", F)))
  
  print(summary |> filter(variable %in% parameter_list))
}
```

#### Table 3, pd (probability of direction)
```{r}
parameter_list_2way_mixed_anova <- c(
  # group parameters
  "muBd_Condition", "lamBd_Condition", "sigD_Condition", # Condition = difficulty
  "muD", "mu_c2","mu_beta1","muBd_interaction" # beta1 = instruction
)

plot_mcmc("hmetad_pre_between_condition_within_difficulty_exp2_revise_summary_Bayes_metad_2way_mixed_ANOVA", 
          "hmetad_pre_between_condition_within_difficulty_exp2_revise_draws_Bayes_metad_2way_mixed_ANOVA", 
          parameter_list_2way_mixed_anova)

plot_mcmc("hmetad_between_condition_within_difficulty_exp2_revise_summary_Bayes_metad_2way_mixed_ANOVA", 
          "hmetad_between_condition_within_difficulty_exp2_revise_draws_Bayes_metad_2way_mixed_ANOVA", 
          parameter_list_2way_mixed_anova)
```

```{r}
parameter_list_2way_mixed_anova <- c(
  # group parameters
  "muBd_Condition", "lamBd_Condition", "sigD_Condition", # Condition = difficulty
  "muD", "mu_c2","mu_beta1","muBd_interaction" # beta1 = instruction
)

plot_mcmc("hmetad_pre_between_condition_within_difficulty_exp2_fix_behavior_few_trial_half_accuracy_fix_bet_cnf_summary_Bayes_metad_2way_mixed_ANOVA", 
          "hmetad_pre_between_condition_within_difficulty_exp2_fix_behavior_few_trial_half_accuracy_fix_bet_cnf_draws_Bayes_metad_2way_mixed_ANOVA", 
          parameter_list_2way_mixed_anova)

plot_mcmc("hmetad_between_condition_within_difficulty_exp2_fix_behavior_few_trial_half_accuracy_fix_bet_cnf_summary_Bayes_metad_2way_mixed_ANOVA", 
          "hmetad_between_condition_within_difficulty_exp2_fix_behavior_few_trial_half_accuracy_fix_bet_cnf_draws_Bayes_metad_2way_mixed_ANOVA", 
          parameter_list_2way_mixed_anova)
```

### plot 95% HDI
```{r}
plot_95pt_ci <- function(draws_name, order, criteria) {
  tar_load(draws_name)
  draws <- get(draws_name) %>%
      select(
        all_of(starts_with("mu"))
      ) |> 
    rename(
      Interaction = muBd_interaction,
      Instruction = mu_beta1,
      Difficulty = muBd_Condition,
    )
  pars <- c("Instruction","Difficulty","Interaction")
  mcmc_intervals_data(
    draws, 
    pars = pars, 
    prob = 0.9,
    prob_outer = 0.95
  ) |> print()
  color_scheme_set("gray")
  p <- mcmc_areas(
    draws,
    pars = pars,
    prob = 0.95,
    border_size = 2,
  ) + xlab("Parameter value") + ylab("Parameters") + theme_pubr(base_size = 24)
  plot(p)
  ggsave(paste0("figure/pdf/posterior_dist_",order,"_exp2_",criteria,".pdf"), dpi = 600, width = 8, height = 5)

}
```

#### Figure 3 left, Table 3
```{r}
plot_95pt_ci("hmetad_pre_between_condition_within_difficulty_exp2_revise_draws_Bayes_metad_2way_mixed_ANOVA", "pre", "revise")
plot_95pt_ci("hmetad_between_condition_within_difficulty_exp2_revise_draws_Bayes_metad_2way_mixed_ANOVA", "post", "revise")
```

```{r}
plot_95pt_ci("hmetad_pre_between_condition_within_difficulty_exp2_fix_behavior_few_trial_half_accuracy_fix_bet_cnf_draws_Bayes_metad_2way_mixed_ANOVA", "pre", "fix_behavior_few_trial_half_accuracy_fix_bet_cnf")
plot_95pt_ci("hmetad_between_condition_within_difficulty_exp2_fix_behavior_few_trial_half_accuracy_fix_bet_cnf_draws_Bayes_metad_2way_mixed_ANOVA", "post", "fix_behavior_few_trial_half_accuracy_fix_bet_cnf")
```

### plot individuals
```{r}
plot_individual_metad <- function(summary_name, data_name, order, criteria) {
  tar_load(summary_name)
  tar_load(data_name)
  summary <- get(summary_name)
  data <- get(data_name)
  
  indiv_draws <- summary %>%
    separate(variable, into = c("name", "idx"), sep = "\\[") %>%
    separate(idx, into = c("id", "difficulty"), sep = ",") %>%
    mutate(
      difficulty = as.numeric(str_sub(difficulty, end = -2)),
    ) %>%
    drop_na(id,difficulty) %>%
    group_by(name,difficulty) %>%
    mutate(
      condition = data$cov,
      condition = if_else(condition == 0, "bet", "cnf")
    ) %>%
    ungroup() %>%
    mutate(
      difficulty = if_else(
        difficulty %% 2 == 0,
        "low",
        "high"
      )
    ) %>%
    select(name, id, condition, difficulty, mean) %>%
    pivot_wider(names_from = name, values_from = mean) %>%
    # mutate(Mratio = remove_outliers(Mratio)) %>%
    mutate(logMratio = ifelse(logMratio<10 & logMratio > -100, logMratio, NA)) %>%
    rename(`log(Pre-M-ratio)` = logMratio, Difficulty = difficulty, Instruction = condition) %>%
    mutate(
      Difficulty = factor(if_else(
        Difficulty == "low",
        "Easy",
        "Hard"
      )),
      Instruction = factor(if_else(
        Instruction == "bet",
        "Bet",
        "Confidence"), levels = c("Confidence", "Bet"))
    )
  
  p <- plot_between_two_condition_for_paper(indiv_draws, "log(Pre-M-ratio)", "Instruction", "Difficulty", c("Confidence", "Bet"))
  plot(p)
  
  ggsave(paste0("figure/pdf/",order,"_logMratio_exp2_",criteria,".pdf"), dpi = 600, width = 5, height = 5)
}
```

#### Figure 3 right
```{r}
plot_individual_metad("hmetad_pre_between_condition_within_difficulty_exp2_revise_summary_Bayes_metad_2way_mixed_ANOVA", 
                      "hmetad_pre_between_condition_within_difficulty_exp2_revise_data", 
                      "pre", "revise")
plot_individual_metad("hmetad_between_condition_within_difficulty_exp2_revise_summary_Bayes_metad_2way_mixed_ANOVA", 
                      "hmetad_between_condition_within_difficulty_exp2_revise_data", 
                      "post", "revise")
```

```{r}
plot_individual_metad("hmetad_pre_between_condition_within_difficulty_exp2_fix_behavior_few_trial_half_accuracy_fix_bet_cnf_summary_Bayes_metad_2way_mixed_ANOVA", 
                      "hmetad_pre_between_condition_within_difficulty_exp2_fix_behavior_few_trial_half_accuracy_fix_bet_cnf_data", 
                      "pre", "fix_behavior_few_trial_half_accuracy_fix_bet_cnf")
plot_individual_metad("hmetad_between_condition_within_difficulty_exp2_fix_behavior_few_trial_half_accuracy_fix_bet_cnf_summary_Bayes_metad_2way_mixed_ANOVA", 
                      "hmetad_between_condition_within_difficulty_exp2_fix_behavior_few_trial_half_accuracy_fix_bet_cnf_data", 
                      "post", "fix_behavior_few_trial_half_accuracy_fix_bet_cnf")
```