---
title: "Targets pipeline"
author: "Hidekazu Nagamura"
date: "2023-9-4"
format: 
  html:
    code-fold: true
---

## Settings

```{r setup}
library(targets)
library(jagstargets)
library(tarchetypes)
library(tidyverse)
library(bayesplot)
library(here)
library(ggpubr)
library(ggpp)
library(ggrain)
library(ggdist)
library(see)
library(patchwork)
library(abind)
library(brms)
library(stats)
library(rstatix)
library(mc2d)
library(parallel)
library(crew)
library(ggnewscale)
library(RColorBrewer)
source("R/functions.R")
```

```{targets settings, tar_globals = TRUE, tar_interactive = FALSE}
library(jagstargets)
library(tarchetypes)
library(here)
tar_option_set(packages = c("tarchetypes","here","tidyverse","rstatix","rjags","ggpubr","readxl","dlookr","ggrain","patchwork","bayesplot","abind","bayestestR","brms"))
source("R/functions.R")
```

## Non-interactive mode
```{r}
tar_visnetwork()
```

### make
```{r}
tar_option_set(error = "continue", memory = "transient", garbage_collection = TRUE, storage = "worker", retrieval = "worker", format = "qs", controller = crew_controller_local(workers = 30, seconds_idle = 3))
# tar_watch(seconds = 10, outdated = FALSE, targets_only = TRUE)
tar_make(seconds_meta_append = 15, seconds_reporter = 5)
```

## read & preprocess data
- exclusion
  - remove only response `nan` or reaction time less than 100 ms
  - remove participants who fixed any responses in each condition
  - remove participants who had fewer than 18 trials in each condition
  
```{targets preprocess_exp2_revision_241224, tar_interactive = FALSE}
list(
  tar_target(data_exp2, get_raw_data_exp2(), deployment = "main"),
  tar_target(subj_info_exp2, get_subject_info_exp2()),
  tar_target(preprocess_exp2_revise, 
             preprocess_data(
               data_exp2, c("condition","difficulty"),
               remove_fix_behavior = TRUE, 
               remove_few_trial_participants = TRUE, 
               remove_half_accuracy = FALSE,
               remove_fix_bet_correctness = FALSE, 
               remove_fix_cnf_correctness = FALSE
               ))
)
```


## analysis
create dataframe in each condition and difficulty
```{targets analysis_for_revision, tar_interactive = FALSE}
list(
  tar_target(
    dataframe_condition_difficulty_revise,
    summarise_data(preprocess_exp2_revise |> mutate(bet=bet-1), c("id", "difficulty", "condition"))
  ),
  tar_target(
    dataframe_bet_revise,
    summarise_data(preprocess_exp2_revise |> mutate(bet=bet-1), c("id", "bet"))
  )
)
```

```{r}
print_sample_size <- function(dataframe_name) {
  original_sample_size <- 237
  tar_load(!!sym(dataframe_name))
  dataframe <- get(dataframe_name)
  tar_load(subj_info_exp2)

  subj_data <- dataframe |> select(id, condition) |> unique() |> 
    left_join(subj_info_exp2, by = "id")
  
  sample_size <- subj_data |> nrow()
  n_bet <- subj_data |> filter(condition == "bet") |> nrow()
  n_cnf <- subj_data |> filter(condition == "cnf") |> nrow()
  n_female <- subj_data |> filter(sex == "female") |> nrow()
  n_male   <- subj_data |> filter(sex == "male")   |> nrow()
  age_mean <- subj_data |> pull(age) |> mean() |> round(1)
  age_sd   <- subj_data |> pull(age) |> sd() |> round(1)
  age_min  <- subj_data |> pull(age) |> min()
  age_max  <- subj_data |> pull(age) |> max()
  
  print(paste0("N = ", sample_size," (",round(sample_size/original_sample_size*100),"% of ", original_sample_size , ")"))
  print(paste0("Confidence: N = ", n_cnf, "; Bet: N = ", n_bet))
  print(paste0("female: N = ", n_female, "; male: N = ", n_male))
  print(paste0("aged ", age_min, "-", age_max, " years"))
  print(paste0(age_mean, "±", age_sd, " (mean±SD) years"))
}
```

### Participant & Table 1

```{r}
print_sample_size("preprocess_exp2_revise")
```

```{r}
basic_analysis_for_revision <- function(dataframe_name, criteria) {
  tar_load(!!sym(dataframe_name))
  
  # arrange dataframe for JASP
  dataframe <- get(dataframe_name)
  dataframe |> 
    pivot_wider(id_cols = c(id, condition), names_from = difficulty, values_from = c(accuracy, bet, cnf, pre_auroc2, post_auroc2, d1, score, bet_rt, ans_rt, cnf_rt)) |> 
    write_csv(here(paste0("csv/dataframe_condition_difficulty_exp2_",criteria,".csv")))
  
  # rename columns for creating figures
  dataframe <- get(dataframe_name) |> 
    rename(
      Difficulty = difficulty, 
      Group = condition,
      Accuracy = accuracy,
      `P(Pre-rating = High)` = bet,
      `Post-rating` = cnf,
      `d'` = d1,
      Score = score
    ) |> 
    mutate(
      Difficulty = factor(if_else(
        Difficulty == "low",
        "Easy",
        "Hard"
      )),
      Group = factor(if_else(
        Group == "bet",
        "Bet",
        "Confidence"
      ), levels = c("Confidence","Bet"))
    )
  
  # plot
  y <- c("Accuracy","d'","c1","P(Pre-rating = High)","Post-rating","Score","bet_rt","ans_rt","cnf_rt")
  pos <- position_dodgenudge(width = 0.2, direction = "split.x")
  for (yy in y) {
    p <- plot_between_two_condition_for_paper(dataframe, yy, "Group", "Difficulty", c("Confidence", "Bet"))
    plot(p)
  
    ggsave(paste0("figure/pdf/",yy,"_exp2_",criteria,".pdf"), dpi = 600, width = 5, height = 5)
  }
  
  # statistical tests
  # dataframe |> 
  #   anova_test(Accuracy ~ Group * Difficulty)
  # dataframe |> 
  #   anova_test(`P(Pre-rating = High)` ~ Group * Difficulty)
  # dataframe |> 
  #   anova_test(`Post-rating` ~ Group * Difficulty)
  ## for inter-participant variance
  dataframe |> 
    group_by(Difficulty) |>
    levene_test(`P(Pre-rating = High)` ~ Group) |> 
    adjust_pvalue()
}
```

### Figure 2
```{r}
basic_analysis_for_revision("dataframe_condition_difficulty_revise", "revise")
```

```{r}
cnf_analysis_by_bet <- function(dataframe_name, criteria) {
  tar_load(!!sym(dataframe_name))
  
  # arrange dataframe for JASP
  dataframe <- get(dataframe_name)
  
  dataframe |> 
    pivot_wider(id_cols = c(id), names_from = bet, values_from = c(accuracy, cnf, pre_auroc2, post_auroc2, d1, score, bet_rt, ans_rt, cnf_rt)) |> 
    write_csv(here(paste0("csv/dataframe_bet_",criteria,"_exp2_revise.csv")))
  
  dataframe <- dataframe |> 
    rename(
      Accuracy = accuracy,
      `Pre-rating` = bet,
      `Post-rating` = cnf,
      `d'` = d1,
      Score = score
    ) |> 
    mutate(
      `Pre-rating` = factor(if_else(
        `Pre-rating` == 0,
        "Low",
        "High"
      ), levels = c("Low", "High"))
    )
  
  p <- plot_within_one_condition_for_paper(dataframe, "Post-rating", "Pre-rating")
  plot(p)
  
  ggsave(paste0("figure/pdf/fig4_exp2_",criteria,".pdf"), dpi = 600, width = 5, height = 5)
  
}
```


### Figure 4
```{r}
cnf_analysis_by_bet("dataframe_bet_revise", "revise")
```

## calculate meta-d'

### condition x difficulty

two-way mixed ANOVA
- within: difficulty
- between: condition

#### pre-M-ratio

```{targets preprocess_metad_pre_between_condition_within_difficulty_exp2_for_revision, tar_interactive = FALSE}
list(
  tar_target(
    preprocess_metad_pre_between_condition_within_difficulty_exp2_revise,
    preprocess_metad_bet_2way_mixed_anova(preprocess_exp2_revise, c("condition", "difficulty"))
  )
)
```

```{targets metad_pre_between_condition_within_difficulty_exp2_for_revision, tar_interactive = FALSE}
list(
  tar_jags(
    hmetad_pre_between_condition_within_difficulty_exp2_revise,
    jags_files = "jags/Bayes_metad_2way_mixed_ANOVA.txt",
    parameters.to.save = c("muBd_Condition", "lamBd_Condition", "sigD_Condition", "muBd_Condition_prior",
                           "muBd_interaction", "lamBd_interaction", "sigD_interaction", "muBd_interaction_prior",
                           "mu_beta1", "mu_beta1_prior",
                           "Mratio","logMratio","muD","mu_c2","mu_regression",
                           "Bd_Condition","Bd_interaction", "beta1","mu","d1","c1"),
    data = preprocess_metad_pre_between_condition_within_difficulty_exp2_revise,
    n.cluster = 3,
    n.chains = 3,
    n.iter = 10000,
    n.burnin = 1000,
    n.thin = 1,
    refresh = 200,
    error = "continue", 
    progress.bar = "gui"
  )
)
```

#### post-M-ratio

```{targets preprocess_metad_between_condition_within_difficulty_exp2_for_revision, tar_interactive = FALSE}
list(
  tar_target(
    preprocess_metad_between_condition_within_difficulty_exp2_revise,
    preprocess_metad_2way_mixed_anova(preprocess_exp2_revise, c("condition", "difficulty"))
  )
)
```

```{targets metad_between_condition_within_difficulty_exp2_for_revision, tar_interactive = FALSE}
list(
  tar_jags(
    hmetad_between_condition_within_difficulty_exp2_revise,
    jags_files = "jags/Bayes_metad_2way_mixed_ANOVA.txt",
    parameters.to.save = c("muBd_Condition", "lamBd_Condition", "sigD_Condition", "muBd_Condition_prior",
                           "muBd_interaction", "lamBd_interaction", "sigD_interaction", "muBd_interaction_prior",
                           "mu_beta1", "mu_beta1_prior",
                           "Mratio","logMratio","muD","mu_c2","mu_regression",
                           "Bd_Condition","Bd_interaction", "beta1","mu","d1","c1"),
    data = preprocess_metad_between_condition_within_difficulty_exp2_revise,
    n.cluster = 3,
    n.chains = 3,
    n.iter = 10000,
    n.burnin = 1000,
    n.thin = 1,
    refresh = 200,
    error = "continue", 
    progress.bar = "gui"
  )
)
```

### plot mcmc
```{r}
plot_mcmc <- function(summary_name, draws_name, parameter_list) {
  tar_load(summary_name)
  tar_load(draws_name)
  summary <- get(summary_name)
  draws <- get(draws_name)
  
  check_mcmc(summary, draws, parameter_list)
  # view(summary)
  print(paste0("Instruction: pd = ",   calculate_pd(draws, "mu_beta1", F)))
  print(paste0("Difficulty: pd = ",  calculate_pd(draws, "muBd_Condition", F)))
  print(paste0("Interaction: pd = ", calculate_pd(draws, "muBd_interaction", F)))
  
  print(summary |> filter(variable %in% parameter_list))
}
```

#### Table 3, pd (probability of direction)
```{r}
parameter_list_2way_mixed_anova <- c(
  # group parameters
  "muBd_Condition", "lamBd_Condition", "sigD_Condition", # Condition = difficulty
  "muD", "mu_c2","mu_beta1","muBd_interaction" # beta1 = instruction
)

plot_mcmc("hmetad_pre_between_condition_within_difficulty_exp2_revise_summary_Bayes_metad_2way_mixed_ANOVA", 
          "hmetad_pre_between_condition_within_difficulty_exp2_revise_draws_Bayes_metad_2way_mixed_ANOVA", 
          parameter_list_2way_mixed_anova)

plot_mcmc("hmetad_between_condition_within_difficulty_exp2_revise_summary_Bayes_metad_2way_mixed_ANOVA", 
          "hmetad_between_condition_within_difficulty_exp2_revise_draws_Bayes_metad_2way_mixed_ANOVA", 
          parameter_list_2way_mixed_anova)
```

### plot 95% HDI
```{r}
plot_95pt_ci <- function(draws_name, order, criteria) {
  tar_load(draws_name)
  draws <- get(draws_name) %>%
      select(
        all_of(starts_with("mu"))
      ) |> 
    rename(
      Interaction = muBd_interaction,
      Instruction = mu_beta1,
      Difficulty = muBd_Condition,
    )
  pars <- c("Instruction","Difficulty","Interaction")
  mcmc_intervals_data(
    draws, 
    pars = pars, 
    prob = 0.9,
    prob_outer = 0.95
  ) |> print()
  color_scheme_set("gray")
  p <- mcmc_areas(
    draws,
    pars = pars,
    prob = 0.95,
    border_size = 2,
  ) + xlab("Parameter value") + ylab("Parameters") + theme_pubr(base_size = 24)
  plot(p)
  ggsave(paste0("figure/pdf/posterior_dist_",order,"_exp2_",criteria,".pdf"), dpi = 600, width = 8, height = 5)

}
```

#### Figure 3 left, Table 3
```{r}
plot_95pt_ci("hmetad_pre_between_condition_within_difficulty_exp2_revise_draws_Bayes_metad_2way_mixed_ANOVA", "pre", "revise")
plot_95pt_ci("hmetad_between_condition_within_difficulty_exp2_revise_draws_Bayes_metad_2way_mixed_ANOVA", "post", "revise")
```

### plot individuals
```{r}
plot_individual_metad <- function(summary_name, data_name, order, criteria) {
  tar_load(summary_name)
  tar_load(data_name)
  summary <- get(summary_name)
  data <- get(data_name)
  
  indiv_draws <- summary %>%
    separate(variable, into = c("name", "idx"), sep = "\\[") %>%
    separate(idx, into = c("id", "difficulty"), sep = ",") %>%
    mutate(
      difficulty = as.numeric(str_sub(difficulty, end = -2)),
    ) %>%
    drop_na(id,difficulty) %>%
    group_by(name,difficulty) %>%
    mutate(
      condition = data$cov,
      condition = if_else(condition == 0, "bet", "cnf")
    ) %>%
    ungroup() %>%
    mutate(
      difficulty = if_else(
        difficulty %% 2 == 0,
        "low",
        "high"
      )
    ) %>%
    select(name, id, condition, difficulty, mean) %>%
    pivot_wider(names_from = name, values_from = mean) %>%
    # mutate(Mratio = remove_outliers(Mratio)) %>%
    mutate(logMratio = ifelse(logMratio<10 & logMratio > -100, logMratio, NA)) %>%
    rename(`log(Pre-M-ratio)` = logMratio, Difficulty = difficulty, Instruction = condition) %>%
    mutate(
      Difficulty = factor(if_else(
        Difficulty == "low",
        "Easy",
        "Hard"
      )),
      Instruction = factor(if_else(
        Instruction == "bet",
        "Bet",
        "Confidence"), levels = c("Confidence", "Bet"))
    )
  
  p <- plot_between_two_condition_for_paper(indiv_draws, "log(Pre-M-ratio)", "Instruction", "Difficulty", c("Confidence", "Bet"))
  plot(p)
  
  ggsave(paste0("figure/pdf/",order,"_logMratio_exp2_",criteria,".pdf"), dpi = 600, width = 5, height = 5)
}
```

#### Figure 3 right
```{r}
plot_individual_metad("hmetad_pre_between_condition_within_difficulty_exp2_revise_summary_Bayes_metad_2way_mixed_ANOVA", 
                      "hmetad_pre_between_condition_within_difficulty_exp2_revise_data", 
                      "pre", "revise")
plot_individual_metad("hmetad_between_condition_within_difficulty_exp2_revise_summary_Bayes_metad_2way_mixed_ANOVA", 
                      "hmetad_between_condition_within_difficulty_exp2_revise_data", 
                      "post", "revise")
```
